### 2015-12-28 introduction.tex
Minor fixes

Scale-free versions of \textsc{MD} include \textsc{AdaGrad
MD}~\cite{Duchi-Hazan-Singer-2011} and~\textsc{Optimistic
MD}~\cite{Rakhlin-Sridharan-2013}. However, these algorithms have non-trivial
regret bounds only when the Bregman divergence associated with the regularizer
is bounded. In particular, since a bound on the Bregman divergence implies that
decision set is bounded, the regret bounds are vacuous for unbounded sets.  In
fact, as we show in Section~\ref{subsection:mirror-descent-lower-bound}
\textsc{AdaGrad MD} and similar algorithms based on \textsc{MD} have
$\Omega(T)$ regret if the Bregman divergence is not bounded.

@@

For unbounded decision sets no scale-free algorithm with a non-trivial regret
bound was known. Unbounded decision sets are practically important, since
learning of large-scale linear models (e.g. logistic regression) is done by
gradient methods that can be reduced to OLO with decision set $\R^d$.

@@

We prove that the regret of \textsc{AdaFTRL} and \textsc{SOLO FTRL} after $T$
rounds is bounded by $O \left(\sqrt{\sup_{v \in K} f(v)
\sum_{t=1}^T\|\ell_t\|_*^2} \right)$ where $f$ is a non-negative regularizer
that is $1$-strongly convex with respect to a norm $\|\cdot\|$ and
$\|\cdot\|_*$ is its dual norm. For \textsc{Scale-Free MD}, we prove $O
\left(\sqrt{\sup_{u,v \in K} B_f(u,v) \sum_{t=1}^T\|\ell_t\|_*^2} \right)$
where $B_f$ is the Bregman divergence associated with a $1$-strongly convex
regularizer $f$.  As we discuss, in Section~\ref{section:mirror-descent}, the
upper bound for \textsc{Scale-Free MD} is never better than the bound for bound
for \textsc{AdaFTRL} and \textsc{SOLO FTRL}.  In
Section~\ref{section:lower-bound}, we show that the $\sqrt{\sum_{t=1}^T
\|\ell_t\|_*^2}$ term in the bounds term is necessary by proving
$\frac{D}{\sqrt{8}} \sqrt{\sum_{t=1}^T\|\ell_t\|_*^2}$ lower bound on the
regret of any algorithm for OLO for any decision set with diameter $D$ with
respect to the primal norm $\|\cdot\|$.

@@

All three algorithms are \textbf{any-time}, i.e., they do not need to know the
number of rounds in advance and the regret bounds hold for all time steps
simultaneously.

>>>>

Scale-free versions of \textsc{MD} include \textsc{AdaGrad
MD}~\cite{Duchi-Hazan-Singer-2011} and~\textsc{Optimistic
MD}~\cite{Rakhlin-Sridharan-2013}. However, these algorithms have non-trivial
regret bounds only when the Bregman divergence associated with the regularizer
is bounded. In particular, since a bound on the Bregman divergence implies that
the decision set is bounded, the regret bounds for \textsc{AdaGrad MD} and
\textsc{Optimistic MD} are vacuous for unbounded sets. In fact, as we show in
Section~\ref{subsection:mirror-descent-lower-bound}, \textsc{AdaGrad MD} and
similar algorithms based on \textsc{MD} have $\Omega(T)$ regret if the Bregman
divergence is not bounded.

@@

For unbounded decision sets no scale-free algorithm with a non-trivial regret
bound was known. Unbounded decision sets are practically important (see e.g.
\cite{Mcmahan-Holt-Sculley-2013}), since learning of large-scale linear models
(e.g. logistic regression) is done by gradient methods that can be reduced to
OLO with decision set $\R^d$.

@@

We prove that the regret of \textsc{AdaFTRL} and \textsc{SOLO FTRL} after $T$
rounds is bounded by $O \left(\sqrt{\sup_{v \in K} f(v)
\sum_{t=1}^T\|\ell_t\|_*^2} \right)$ where $f$ is a non-negative regularizer
that is $1$-strongly convex with respect to a norm $\|\cdot\|$ and
$\|\cdot\|_*$ is its dual norm. For \textsc{Scale-Free MD}, we prove $O
\left(\sqrt{\sup_{u,v \in K} B_f(u,v) \sum_{t=1}^T\|\ell_t\|_*^2} \right)$
where $B_f$ is the Bregman divergence associated with a $1$-strongly convex
regularizer $f$.  As we discuss, in Section~\ref{section:mirror-descent}, the
upper bound for \textsc{Scale-Free MD} is never better than the bound for bound
for \textsc{AdaFTRL} and \textsc{SOLO FTRL}.  In
Section~\ref{section:lower-bound}, we show that the $\sqrt{\sum_{t=1}^T
\|\ell_t\|_*^2}$ term in the bounds is necessary by proving $\frac{D}{\sqrt{8}}
\sqrt{\sum_{t=1}^T\|\ell_t\|_*^2}$ lower bound on the regret of any algorithm
for OLO for any decision set with diameter $D$ with respect to the primal norm
$\|\cdot\|$.

@@

All three algorithms are \textbf{any-time}, i.e., they do not need to know the
number of rounds, $T$, in advance and the regret bounds hold for all $T$
simultaneously.

### 2015-12-28 preliminaries.tex
Polished grammar and typography.
Minor fixes

In OLO, in each round $t=1,2,\dots$, the algorithm chooses a point $w_t$ in the
decision set $K \subseteq V$ and then the algorithm observes a loss vector
$\ell_t \in V^*$. The instantaneous loss of the algorithm in round $t$ is
$\langle \ell_t, w_t \rangle$. The cumulative loss of the algorithm after $T$
rounds is $\sum_{t=1}^T \langle \ell_t, w_t \rangle$.  The regret of the
algorithm with respect to a point $u \in K$ is
$$
\Regret_T(u) = \sum_{t=1}^T \langle \ell_t, w_t \rangle - \sum_{t=1}^T \langle \ell_t, u \rangle,
$$
and the regret with respect to the best point is $\Regret_T= \sup_{u \in K}
\Regret_T(u)$.  We assume that $K$ is a non-empty closed convex subset of $V$.
Sometimes we will assume that $K$ is also bounded. We denote by $D$ its
diameter with respect to $\|\cdot\|$, i.e. $D = \sup_{u,v \in K} \|u - v\|$. If
$K$ is unbounded, $D = +\infty$.

@@

The \emph{Fenchel conjugate} of a function $f:K \to \R$ is the function
$f^*:V^* \to \R \cup \{+\infty\}$ defined as $f^*(\ell) = \sup_{w \in K} \left(
\langle \ell, w \rangle - f(w) \right)$.  The Fenchel conjugate of any function
is convex (since it is a supremum of affine functions) and satisfies
 the \emph{Fenchel-Young inequality}
$$
\text{$\forall w \in K$, $\forall \ell \in V^*$} \qquad
f(w) + f^*(\ell) \ge \langle \ell, w \rangle \; .
$$

@@

\begin{proposition}[Diameter vs. Range]
\label{proposition:diameter-vs-range}
Let $K \subseteq V$ be a non-empty bounded closed convex subset.  Let $D =
\sup_{u,v \in K} \|u - v\|$ be its diameter with respect to $\|\cdot\|$.  Let
$f:K \to \R$ be a non-negative lower semi-continuous function that is
$1$-strongly convex with respect to $\|\cdot\|$.  Then, $D \le \sqrt{8 \sup_{v
\in K} f(v)}$.
\end{proposition}

@@

\item $f^*$ is $\frac{1}{\lambda}$-strongly smooth i.e. for any $x,y \in V^*$, $\Breg_{f^*}(x, y) \le \frac{1}{2\lambda} \|x - y\|_*^2$.

\item $f^*$ has $\frac{1}{\lambda}$-Lipschitz continuous gradients i.e.
for any $x,y \in V^*$,
$\|\grad f^*(x) - \grad f^*(y)\| \le \frac{1}{\lambda} \|x - y\|_*$.

>>>>

In OLO, in each round $t=1,2,\dots$, the algorithm chooses a point $w_t$ in the
decision set $K \subseteq V$ and then the algorithm observes a loss vector
$\ell_t \in V^*$. The instantaneous loss of the algorithm in round $t$ is
$\langle \ell_t, w_t \rangle$. The cumulative loss of the algorithm after $T$
rounds is $\sum_{t=1}^T \langle \ell_t, w_t \rangle$.  The regret of the
algorithm with respect to a point $u \in K$ is
$$
\Regret_T(u) = \sum_{t=1}^T \langle \ell_t, w_t \rangle - \sum_{t=1}^T \langle \ell_t, u \rangle,
$$
and the regret with respect to the best point is $\Regret_T= \sup_{u \in K}
\Regret_T(u)$.  We assume that $K$ is a non-empty closed convex subset of $V$.
Sometimes we will assume that $K$ is also bounded. We denote by $D$ its
diameter with respect to $\|\cdot\|$, i.e., $D = \sup_{u,v \in K} \|u - v\|$.
If $K$ is unbounded, $D = +\infty$.

@@

The \emph{Fenchel conjugate} of a function $f:K \to \R$ is the function
$f^*:V^* \to \R \cup \{+\infty\}$ defined as $f^*(\ell) = \sup_{w \in K} \left(
\langle \ell, w \rangle - f(w) \right)$.  The Fenchel conjugate of any function
is convex (since it is a supremum of affine functions) and satisfies
 the \emph{Fenchel-Young inequality}
$$
\forall w \in K, \ \forall \ell \in V^* \qquad \qquad
f(w) + f^*(\ell) \ge \langle \ell, w \rangle \; .
$$

@@

\begin{proposition}[Diameter vs. Range]
\label{proposition:diameter-vs-range}
Let $K \subseteq V$ be a non-empty bounded closed convex set.  Let $D =
\sup_{u,v \in K} \|u - v\|$ be its diameter with respect to $\|\cdot\|$.  Let
$f:K \to \R$ be a non-negative lower semi-continuous function that is
$1$-strongly convex with respect to $\|\cdot\|$.  Then, $D \le \sqrt{8 \sup_{v
\in K} f(v)}$.
\end{proposition}

@@

\item $f^*$ is $\frac{1}{\lambda}$-strongly smooth, i.e., for any $x,y \in
V^*$, $\Breg_{f^*}(x, y) \le \frac{1}{2\lambda} \|x - y\|_*^2$.

\item $f^*$ has $\frac{1}{\lambda}$-Lipschitz continuous gradients, i.e.,
for any $x,y \in V^*$,
$\|\grad f^*(x) - \grad f^*(y)\| \le \frac{1}{\lambda} \|x - y\|_*$.
